Summary Tables

### 2019-04-28 summary_tables.Rmd

for(city in cities){
  count_people <- nrow(io[[city]]$synth_pop)
    td <- io[[city]]$dur %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, funs(round((.) / count_people, round_to)))
    colnames(td)[3:7] <- rownames(scen_prop)
    print(kable(td, caption = paste("Duration table (mins) for ", city, "( ", count_people, " ) per person")))
    cat("\n")
}

>>>>

for(city in cities){
  count_people <- nrow(io[[city]]$synth_pop)
    td <- io[[city]]$dur %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, funs(round((.) / count_people, round_to)))
    colnames(td)[3:7] <- rownames(scen_prop)
    print(kable(td, caption = paste("Duration table (mins) for ", city, "( ", count_people, " ) per person (everyone)")))

    count_people <- length(unique(io[[city]]$trip_scen_sets$participant_id))
    td <- io[[city]]$dur %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, funs(round((.) / count_people, round_to)))
    colnames(td)[3:7] <- rownames(scen_prop)
    print(kable(td, caption = paste("Duration table (mins) for ", city, "( ", count_people, " ) per person (people with trips)")))
    cat("\n")
}
